B\'{e}zier $\bar{B}$ projection

### 2017-12-20 projection1120.tex
update

\added{The relationship of $\bar{B}$-formulation with mixed formulations has been studied and proved to be equivalent by Simo and Hughes \cite{hughes_variational_1986}. However, the symmetric \Bezier $\bar{B}$ projection lacks the connection to the mixed formulation. For this reason, instead of considering $\bar{B}$ formulation as a strain projection method, we regard it as a mixed formulation with the auxiliary variable ( the shear stress for the case of Timoshenko beam) being eliminated and use the \Bezier dual basis functions as the test functions of the auxiliary variable. Since the resulting stiffness matrix is not symmetric, this formulation is refered to as non-symmetric \Bezier $\bar{B}$ projection.}

@@

\added{The contour plots of $\sigma_{xx}$ for bicubic elements of the third mesh are shown in Figure \ref{fig:platewithhole_contour}, $Q_3$ elements are severely locked while all $\bar{B}$ methods converge to the reference solution. }
\begin{figure}[h]
    \center
\begin{tabular}{ccc}
\includegraphics[width=.33\linewidth]{deformation_p_2} & \includegraphics[width=.33\linewidth]{deformation_p_3} & \includegraphics[width=.33\linewidth]{deformation_p_4}\\
\includegraphics[width=.33\linewidth]{stress_p_2} & \includegraphics[width=.33\linewidth]{stress_p_3} & \includegraphics[width=.33\linewidth]{stress_p_4}\\
\includegraphics[width=.33\linewidth]{energy_p_2} & \includegraphics[width=.33\linewidth]{energy_p_3} & \includegraphics[width=.33\linewidth]{energy_p_4}
\end{tabular}
    \caption{Convergence study of the plate with a circular hole. The relative $L^2$ error of displacement, stress and the relative error in energy norm with respect to mesh refinement.}
	\label{fig:platewithhole_convergence}
\end{figure}

>>>>

\added{The relationship of $\bar{B}$-formulation with mixed formulations has been studied and proved to be equivalent by Simo and Hughes \cite{hughes_variational_1986}. However, the symmetric \Bezier $\bar{B}$ projection lacks the connection to the mixed formulation. For this reason, instead of considering $\bar{B}$ formulation as a strain projection method, we regard it as a mixed formulation with the auxiliary variable ( the shear stress for the case of Timoshenko beam) being eliminated. Owing to the dual basis formulation of \Bezier projection operator, we use the \Bezier dual basis functions as the test functions of the auxiliary variable. Since the resulting stiffness matrix is not symmetric, this formulation is refered to as non-symmetric \Bezier $\bar{B}$ projection.}

@@

\added{The contour plots of $\sigma_{xx}$ for bicubic elements of the third mesh are shown in Figure \ref{fig:platewithhole_contour}, $Q_3$ elements are severely locked while all $\bar{B}$ methods converge to the reference solution. }
\begin{figure}[h]
    \center
\begin{tabular}{ccc}
\includegraphics[width=.31\linewidth]{deformation_p_2} & \includegraphics[width=.31\linewidth]{deformation_p_3} & \includegraphics[width=.31\linewidth]{deformation_p_4}\\
\includegraphics[width=.31\linewidth]{stress_p_2} & \includegraphics[width=.31\linewidth]{stress_p_3} & \includegraphics[width=.31\linewidth]{stress_p_4}\\
\includegraphics[width=.31\linewidth]{energy_p_2} & \includegraphics[width=.31\linewidth]{energy_p_3} & \includegraphics[width=.31\linewidth]{energy_p_4}
\end{tabular}
    \caption{Convergence study of the plate with a circular hole. The relative $L^2$ error of displacement, stress and the relative error in energy norm with respect to mesh refinement.}
	\label{fig:platewithhole_convergence}
\end{figure}
